\appendix
\section{Appendix}
\label{appendixA}

The details of our questionnaire are presented below. Our questions focused on the HPC load, power variability and demand management approaches. 

\begin{enumerate}
\item{What is your total facility energy? This should be the same as the total facility energy number that is used for calculating PUE.}
\item{ What is your total HPC load?}
\item{What is your facility PUE?}
\item{What is your facility's theoretical peak energy, as the infrastructure is currently fit up?}
%\item{What is the maximum \emph{unscheduled} intra-­hour variation in total facility energy that is likely to re-­occur?}
%\item{What is the maximum \emph{scheduled} intra-­hour variation in total facility energy that is likely to re-­occur?}
\item{What is the maximum intra-­hour variation in total facility energy that is likely to re-­occur?}
\item{Do you employ coarse-grained power management strategies?}
\item{Do you employ fine-grained power management strategies?}
\item{Do you employ load migration as a strategy?}
\item{Do you employ job scheduling as a strategy?}
\item{Do you employ back-up scheduling as a strategy?}
\item{Do you employ shutdown as a strategy?}
\item{Do you employ lighting control as a strategy?}
\item{Do you employ increasing air temperature as a strategy?}
\item{Do you employ liquid temperature adjustment as a strategy?}
\item{Do you cut jobs as a strategy?}
\item{Are there any other strategies that you employ to manage and control your total facility energy in response to a request from your energy utility/provider?}
\item{Please evaluate each of the above strategies from questions 7 to 16 as high, medium or low, based on the MW impact of each of these strategies as a response to a grid request.}
\item{Have you had conversations with your electricity service provider about peak shedding?}
\item{Have you had conversations with your electricity service provider about peak shifting?}
\item{Have you had conversations with your electricity service provider about dynamic pricing?}
\item{Have you had conversations with your electricity service provider about grid scale storage?}
\item{Have you had conversations with your electricity service provider about power variability related to renewables and methods used for responding to such variability?}
\item{Have you had conversations with your electricity service provider about frequency response?}
\item{Have you had conversations with your electricity service provider about regulation?}
\item{Have you had conversations with your electricity service provider about congestion?}
\item{Is there information you would like from your provider that you are not getting? If yes, please describe what you would like to know.}
\item{Is your provider asking for information from you that you are not able to provide? If yes, please describe what they are asking for.}
\item{Do you experience any power quality issues at your HPC facility? If yes, please describe.}
\item{Do you know of any consequences between your site and your provider from either scheduled or un­scheduled intra-­hour power variations?}
\item{Please evaluate as high, medium or low the following motivations for your site's interest in pursuing a stronger relationship with your electricity service provider.}
\item{ Please help us understand the economic aspects of power saving strategies. This is an open ended question and we encourage any feedback. For instance, what might it take to induce your site to participate in programs offered by your electricity service provider? What are the trade­offs between savings and loss of scientific productivity and equipment depreciation.}
\end{enumerate}


